\documentclass{pl_template}  % 使用自定义的类文件
\usepackage{ulem}
\usepackage{soul}

\begin{document}

\firstpageheader


% 首页内容
\begin{center}
    \today
\end{center}

\vspace{2em}
\raggedright{  % 左对齐
VIA USPS PRIORITY MAIL\\
USCIS\\
Attn: Premium I-140\\
P.O. Box 21500\\ 
Phoenix, AZ 85036-1500\\
\vspace{2em}
\textbf{Re: EB-2 Immigrant Petition for Permanent Residency with request for a National Interest Waiver} \\
\textbf{Petitioner/Beneficiary:} \Petitioner\\
\textbf{Type of Petition:} I-140, EB-2 National Interest Waiver\\
\textbf{Classification Sought:}  Immigration and Nationality Act 203(b)(2)(B) \\
}

\vspace{3em}

\noindent Dear USCIS Officer:

\hspace*{2em} Please be advised that the undersigned counsel represents the above-referenced Petitioner/Beneficiary \textbf{\MrMs.\  \Petitioner} (“Petitioner”) in \HisHerLow \   immigration matters. This letter is respectfully submitted in support of Petitioner’s Immigrant Petition for Alien Worker (I-140).

\hspace*{2em}Petitioner is eligible for EB-2 classification as a member of the professions holding an advanced degree under section 203(b)(2) of the Immigration and Nationality Act, 8 U.S.C. §1153(b)(2) because Petitioner holds a \textbf{DEGREE UPDATE} Master's degree in Information Systems Management from Carnegie Mellon University(Exhibit 1) and a \textbf{DEGREE UPDATE}Bachelor’s degree with a major in Managerial Economics and a minor in Technology Management from the University of California, Davis (Exhibit 2).

\hspace*{2em}Petitioner believes that \HeSheLow \ should be granted a National Interest Waiver because \HeSheLow \  can demonstrate: (1) \HisHerLow \  proposed endeavor has both substantial merit and national importance; (2) that \HeSheLow is well positioned to advance the proposed endeavor; and (3) that, on balance, it would be beneficial to the United States to waive the job offer and labor certification requirements. \textit{Matter of Dhanasar}, 26 I\&N Dec. 884 (AAO 2016)



%\vspace{2em}
%\newpage
%\firstpageheader

\newpage  % 手动分页
% 其他页面内容
\otherpagesheader  % 设置后续页面的页眉
\tableofcontents
\section{EB-2 Eligibility Statement}
\Petitioner \  qualifies for the EB-2 classification as a professional with an advanced degree. \HeSheUp \ has completed degrees in fields critical to national security and public policy: 
\begin{itemize}
    \item \textbf{University of California, Davis:} Bachelor’s with a major in Managerial Economics and a minor in Technology Management (Exhibit 2).
    \item \textbf{Carnegie Mellon University:} Master of Science in Information Systems (Exhibit 1). 
\end{itemize}
These academic credentials affirm \Petitioner’s expertise and support \HisHerLow \ eligibility for the EB-2 classification.

% START INSERTION


\letterclosing  % 在此处插入书信结尾

\vspace{2em}
 
\end{document}
